### 2020-01-04 methods.tex
pre-Activation Maps

which approximates the log $\alpha-$Norm for both Very Heavy Tailed weight matrices ($alpha < 2$  and reasoably well for finite size, Moderately Heavy Tailed ones $\alpha\in[2,5]$.

@@

\begin{figure}[H]
   \centering
   \subfigure[ESD of AlexNet Conv2D Layer 3 Slice 1]{
     \includegraphics[scale=0.5]{img/alexnet1.png} 
     \label{fig:alexnet1}
   }
   \subfigure[ESD of the same matrix, randomly shuffled  ]{
      \includegraphics[scale=0.5]{img/alexnet2.png}
      \label{fig:alexnet2}
   }
   \caption{%
    Caption
   }
   \label{fig:alexnet}
\end{figure}

These plots tell us that the Tensor Slice of the Conv2D contains significant correlations learned from the data.  
By modeling the ESD with a power law distribution $\lambda^{\alpha}$, we can characterize the amount of correlation learned;
the smaller the exponent $\alpha$, the more correlation in the weight matrix.

>>>>

which approximates the log $\alpha-$Norm for both Very Heavy Tailed weight matrices ($\alpha < 2)$  and reasoably well for finite size, Moderately Heavy Tailed ones $\alpha\in[2,5]$.

@@

\begin{figure}[H]
   \centering
   \subfigure[Actual ESD]{
     \includegraphics[scale=0.5]{img/alexnet1.png} 
     \label{fig:alexnet1}
   }
   \subfigure[ESD of randomly shuffled matrix]{
      \includegraphics[scale=0.5]{img/alexnet2.png}
      \label{fig:alexnet2}
   }
   \caption{ESD of AlexNet Conv2D pre-Activation map for Layer 3 Slice 1, actual and randomized}
   \label{fig:alexnet}
\end{figure}

These plots tell us that the pre-activation maps of the Conv2D contains significant correlations learned from the data.  
By modeling the ESD with a power law distribution $\lambda^{\alpha}$, we can characterize the amount of correlation learned;
the smaller the exponent $\alpha$, the more correlation in the weight matrix.
